
::: {.toolbar}
```{r}

selectInput("groupClimate", "Group:", groups_names)
selectInput("iucnClimate", "IUCN Red List Category:", iucn_names)

```

:::

::: {.grid}

::: {.g-col-12 .g-col-md-6}

#### Number of species at thermal risk

The graph shows the number of species at thermal risk for this site under current conditions and three future SSP (shared socio-economic pathways) climate scenarios for 2100. Thermal risk occurs when the site's temperature exceeds a species' thermal limit, defined as the 95th percentile of temperatures where the species has been recorded. Some species, especially in tropical areas, may already exceed this limit. While not indicating local extinction, thermal risk indicates stressful conditions to the organism that may affect its survival.

```{r}
#| title: Number of species at climate risk
shiny::plotOutput("climate_number_species")
```

:::

::: {.g-col-12 .g-col-md-6}

#### Monthly temperature (degrees Celsius) at the site

The graph shows monthly sea temperature trends for different sites, with an option to display data as anomalies compared to a baseline. Each line represents a site, showing seasonal changes and differences between locations. When using anomalies, the graph highlights periods that are warmer or cooler than usual. This helps to understand temperature patterns and possible climate impacts at each site. 
<br><br>

```{r}
#| title: Temperature at sites

layout_column_wrap(
  width = 1,
  heights_equal = "row",
  div(htmltools::tags$span(
      bslib::input_switch("spi_clim_anomaly", 
      htmltools::span(
        "Show anomaly ",
        bslib::tooltip(bsicons::bs_icon("info-circle"),
  "Anomaly is the difference of temperature between that particular point in time and the average across the whole period.")
      )
      , FALSE)), id = "climate-sites-add-control"),
  div(dygraphs::dygraphOutput("climate_temperature_sites"))
)
```

:::
:::

-----

#### Species thermal risk

::: {.callout-note appearance="simple" title="Attention" icon=false}
The following table highlights species that are potentially at thermal risk at this site, based on its current thermal limits. It is important to note that, since the region has not yet experienced the extreme sea temperatures predicted for the future, there is uncertainty about how tropical species—already living near their upper thermal limits—will respond to these unprecedented conditions.
:::

```{r}
#| title: Thermal risk

reactable::reactableOutput("climate_thermal_risk")
```

<br>

The values in the _Current_ and _SSP_ columns represent the temperature difference (in degrees Celsius) between the site temperature and the species' thermal limit. Cells highlighted in <span style="color: #d9905f; font-weight: bold;">orange</span> (positive values) indicate temperatures exceeding the species' thermal limit, placing them at risk. Cells in <span style="color: #a3c2de; font-weight: bold;">blue</span> (negative values) show temperatures below the thermal limit, indicating no immediate thermal risk.

_Depth_ refers to the primary depth zone where the species reside:

- <span style="color: #675292; font-weight: bold;">S</span> (Sea Surface): Includes depths up to 200 m.  
- <span style="color: #b69354; font-weight: bold;">NS</span> (Not limited to Surface): Refers to species capable of inhabiting depths greater than 200 m. For these species, bottom sea temperature is used to evaluate thermal limits.  
- <span style="color: #868686; font-weight: bold;">NA</span> (Not Available): Indicates a lack of database information about the species' depth preference. In such cases, sea surface temperature is used as a proxy.  

The Shared Socioeconomic Pathways (SSPs) describe possible future scenarios based on greenhouse gas emissions and societal development.

- SSP1 (2.6): A "sustainable development" pathway with low emissions, strong international cooperation, and rapid adoption of green technologies. Lower global warming.  
- SSP2 (4.5): A "middle-of-the-road" scenario with moderate emissions. Society follows current trends, with gradual technological improvements and mixed success in climate policies.  
- SSP3 (7.0): A "regional rivalry" pathway with high emissions. Countries prioritize self-interest, leading to limited climate action. Higher global warming.  