
::: {.toolbar}
```{r}

selectInput("groupClimate", "Group:", groups_names)
selectInput("iucnClimate", "IUCN Red List Category:", iucn_names)

```

:::

::: {.grid}

::: {.g-col-12 .g-col-md-6}

#### Number of species in thermal risk

```{r}
#| title: Number of species at climate risk
shiny::plotOutput("climate_number_species")
```

:::

::: {.g-col-12 .g-col-md-6}

#### Temperature at sites

```{r}
#| title: Temperature at sites

layout_column_wrap(
  width = 1,
  heights_equal = "row",
  div(htmltools::tags$span(
      bslib::input_switch("spi_clim_anomaly", "Anomaly", FALSE)), id = "climate-sites-add-control"),
  div(dygraphs::dygraphOutput("climate_temperature_sites"))
)
```

:::
:::

#### Species thermal risk

::: {.callout-note appearance="simple" title="Attention" icon=false}
The following table indicates species that are potentially at thermal risk on the site, considering its current thermal limit. Note that, because on the recent period we have never experienced such high temperatures on the sea as predicted for the future, we do not know exactly how tropical species (that are living close to the upper limits) will actually react to those new temperatures.
:::

```{r}
#| title: Thermal risk

reactable::reactableOutput("climate_thermal_risk")
```

Values on the current and SSP columns is the difference between the site temperature and the species thermal limit. Cells in <span style="color: #d9905f; font-weight: bold;">orange</span> (positive values) are above the thermal limit (thus, at risk), while those in <span style="color: #a3c2de; font-weight: bold;">blue</span> (negative values) are below the thermal limit.

_Depth_ refers to the primary depth zone where the species reside. <span style="color: #675292; font-weight: bold;">S</span> stands for "sea surface" and applies to depths of up to 200m. <span style="color: #b69354; font-weight: bold;">NS</span>  means "not limited to surface" and refers to species that can inhabit areas deeper than 200m. In this case, the sea temperature at the bottom is used to infer the species' thermal limits. <span style="color: #868686; font-weight: bold;">NA</span> indicates "information not available," meaning there is no database information specifying the depth where the species reside. In such cases, the sea surface temperature is used.
