
::: {.toolbar}

```{r}
#selectInput("higherGeographyDiversity", "Site:", sites_names)
selectInput("taxonLevelDiversity", "Rank:", taxonLevels[-c(1,2)])
selectInput("plotType", "Abundance:", plot_type)
```

:::

#### Diversity metrics

This figure shows the number of sequences (also called reads) in each sample after filtering for quality control, both as absolute numbers as well in relative abundance of the total reads. All sequences that received names are colored, the grey area therefore shows reads that could not be resolved to a taxonomic name. You can toggle the taxonomic level that is shown. At each taxonomic level the top 10 most observed taxa receive a distinct color. Note that contaminations from humans, bacteria (and other prokaryotes), fungi and domestic animals have been removed prior to the analysis.  

```{r}
#| title: Taxonomic composition of all samples across the site

uiOutput("tax_bar_plot", style = "height: 500px;")
```

------

::: {.toolbar}
```{r}

 selectInput("taxonLevel", "Taxonomic rank:", choices = taxonLevels)
 selectInput("alpha_measure", "Alpha diversity:", choices = alpha_measure)
 selectInput("beta_measure", "Beta diversity:", choices = beta_measure)

```

:::

::: {.grid}

::: {.g-col-12 .g-col-md-6}

#### Alpha Diversity: How diverse is each sample individually?

This figure presents the alpha diversity of each sample, grouped by location (where samples from the same location are considered replicates). The simplest measure of alpha diversity is the count of species or ASV (Amplicon Sequence Variant) sequences found within a sample. Alpha diversity can also be explored across various taxonomic levels or by including all sequences, even those that are not taxonomically resolved. Additionally, other indices, such as Chao, Shannon, or Simpson, provide more nuanced assessments by incorporating the relative abundance of different taxa or ASV sequences. These measures offer deeper insights into the richness and evenness of species within each sample.

```{r}

plotly::plotlyOutput("alpha_plot")

```

:::

::: {.g-col-12 .g-col-md-6}

#### Beta diversity: How does species composition vary between samples?

Beta diversity measures indicate how similar or different samples are in terms of species composition. To assess this, a distance matrix is generated for all samples, which is then visualised by plotting the distances. In the resulting plot, points that are farther apart represent samples with greater differences in species composition, while points closer together indicate more similar samples. In this context, you may observe that samples collected from the same location tend to cluster together, reflecting their shared characteristics.

```{r}

plotly::plotlyOutput("beta_plot")

```

:::

:::